Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-25 manuscript/manuscript.Rmd
added all 50 data points to rew len graph

```{r timeseries, fig.cap="TBD.", out.width = "6.5in"}
policy_labels <- list("msy" = "MSY Const. Mortality", "tac"= "80% MSY Const. Mortality", "ppo"= "DRL")
policy_labeller <- function(variable,value){
  return(policy_labels[value])
}
msy_tac_ppo |> 
    group_by(rep, policy) |>
    filter(rep == 6) |>
    ggplot(aes(t, abundance, col = species)) + 
        geom_line()  + 
        scale_color_manual(values=c('palegreen3', 'coral1', 'deepskyblue4')) +
        facet_wrap(~factor(policy, levels = c("msy", "tac", "ppo")), labeller = policy_labeller ) +
        labs(y = "abundance", x = "time") +
        theme(aspect.ratio = 2/3)
```

@@

p1 <- msy_tac_ppo |> 
    group_by(rep, policy) |>
    filter(t==max(t), species == "X", rep < 30) |>
    ggplot(aes(rep, t)) + 
      geom_col() +
      facet_wrap(~factor(policy, levels = c("msy", "tac", "ppo")), labeller = policy_labeller ) +
      labs(y = "episode length", x = "repetition") +
      theme(axis.text.x = element_blank())

p2 <- msy_tac_ppo |> 
    group_by(rep, policy) |>
    filter(t==max(t), species == "X", rep < 30) |>
    ggplot(aes(rep, reward)) + 
      geom_col() +
      facet_wrap(~factor(policy, levels = c("msy", "tac", "ppo")), labeller = policy_labeller ) +
      labs(y = "episode harvest", x = "repetition") +
      theme(axis.text.x = element_blank())

>>>>

```{r timeseries, fig.cap="TBD.", out.width = "6.5in"}
policy_labels <- list("msy" = "MSY Const. Mortality", "tac"= "80% MSY Const. Mortality", "ppo"= "DRL")
policy_labeller <- function(variable,value){
  return(policy_labels[value])
}
msy_tac_ppo |> 
    group_by(rep, policy) |>
    filter(rep == 49) |>
    ggplot(aes(t, abundance, col = species)) + 
        geom_line()  + 
        scale_color_manual(values=c('palegreen3', 'coral1', 'deepskyblue4')) +
        facet_wrap(~factor(policy, levels = c("msy", "tac", "ppo")), labeller = policy_labeller ) +
        labs(y = "abundance", x = "time") +
        theme(aspect.ratio = 2/3)
```

@@

p1 <- msy_tac_ppo |> 
    group_by(rep, policy) |>
    filter(t==max(t), species == "X", rep < 50) |>
    ggplot(aes(rep, t)) + 
      geom_col() +
      facet_wrap(~factor(policy, levels = c("msy", "tac", "ppo")), labeller = policy_labeller ) +
      labs(y = "episode length", x = "repetition") +
      theme(axis.text.x = element_blank())

p2 <- msy_tac_ppo |> 
    group_by(rep, policy) |>
    filter(t==max(t), species == "X", rep < 50) |>
    ggplot(aes(rep, reward)) + 
      geom_col() +
      facet_wrap(~factor(policy, levels = c("msy", "tac", "ppo")), labeller = policy_labeller ) +
      labs(y = "episode harvest", x = "repetition") +
      theme(axis.text.x = element_blank())
